The project task was to create and train a \gls{ml} algorithm capable of playing the game \enquote{Bomberman}.
The program, referred to as \enquote{agent} from here on, should be able to run in the Python game environment provided
by Prof.~Koethe in his GitHub repository\cite{githubbase}.
The environment provided takes care of the general game logic, calls all participating agents in order, and communicates
the move returned by every agent with all participants.
For the agent implementation, the main logic should be contained in the \listinline{act()} method of the callbacks.py
file, as it will be the entry point for the game environment.
In the end, every team should create at least two different \gls{ml} models, one of which will be submitted to compete
against the submitted model of every other team.
The project code for our submission, including the entire coding history, is publicly accessible on
GitHub\cite{githubown}.

\subsection{Game Rules}
\label{subsec:rules}
In this version of Bomberman, all agents will be launched into an unknown arena consisting of rectangular grid built
from the following tiles:
\begin{itemize}
  \item Free tiles - these tiles can be moved through and have no further effects.
  \item Agents - these tiles contain an agent and can not be moved through.
  \item Bombs - these tiles indicate the position of a placed bomb amd can be moved through.
  \item Explosion tiles - these tiles destroy any agent contained within them, and spawn around a bomb four time steps
after its placement.
  \item Solid tiles - these tiles can not be moved through.
  \item Crates - these tiles can not be moved through, but they will be destroyed by bombs and can contain coins.
  \item Coins - these tiles can be moved through and contain a coin which can be picked up by entering the tile.
\end{itemize}

Every agent will act in order, its actions will be resolved before the next agent acts, and the goal of the game is to
survive longer than every other participant.
In case of a tie (E.g.~caused by two remaining agents dying to the same bomb), the total score will determine a winner.
Taking out an opponent or collecting coins raises an agents score.

Furthermore, the game is limited to a total of 400 game steps, and every agent has to calculate its next move within
0.5 seconds.
Failure to meet the time limit will be punished by not allowing the offending agent to move on this turn, and the time
taken beyond the limit will be deducted from the agent's next turn timer.
Illegal moves (E.g.~attempting to move into a wall) will be caught by the environment and replaced with a WAIT action
instead.
